Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup
of $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations. We consider the {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, we sharply bound the degree of the generators and
relations for $M(\Gamma)$, for general $\Gamma$ \todo{Peter: Why do you say general gamma?  I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}  \todo{Peter: also, its not clear to me that this should be said right here.  I think we may want to say a bit more about what's already known instead of going directly to what we have done}.  In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
\cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$. In order to find generators and relations for $M(\Gamma)$, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
category, using a generalization of the GAGA principle. By
\cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of
categories between orbifold curves and log stacky curves over $\BC$
. Hence, for the remainder of the paper, we will work in the
algebraic category.

@@

The goal of this paper is to provide a stricter bound on the
generator and relation degrees of log spin canonical rings
for all genera. Note that O'Dorney's bounds are asymptotically
strict for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
to the log spin curve case allows for lower bounds.
The main theorem of this paper is the following improved bound on
the degree of generators and relations of log spin canonical rings:

\todo{State for even weight modular forms attributed to VZB.}
\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere?} so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
geometrically-connected Deligne-Mumford stack of dimension $1$ over
$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
its stabilizers are coprime to char $k$. Throughout this paper,
stacky curves will be assumed to be tame and $k$ will always be
algebraically closed. The language of stacks will be omitted in
this paper, as it is sufficient to view stacky curves and related
objects $\sx$ as a scheme whose associated divisor group allows for
a finite number of \textbf{stacky points} which may be viewed
heuristically as ``fractional points''. See Voight and
Zureick-Brown for more thorough treatment of these definitions
\cite[Chapter 5]{vzb:stacky}.

@@

\begin{defn}
If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.

@@

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_L$ to
represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.

\todo{do this part}
Part on Kodaira--Spencer \cite{kodaira-spencer:deformations}.

@@

\subsection{Junk}
This is stuff that has been moved out of the introduction to possibly
be retooled for this section.

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$).
\end{enumerate}
\end{lem}
\begin{proof}
{\bf Part (a):}
By
Equation ~\ref{eqn:deg1-sat-ind}, for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

\begin{defn}
\label{defn:admissible}
Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
curves, with the same course space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

@@

\begin{align*}
	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ \initial(I))_d \\
	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,
	x_{7, 1}^2 \rangle
\end{align*}

>>>>

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup
of $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations. We consider the {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, we sharply bound the degree of the generators and
relations for $M(\Gamma)$, for general $\Gamma$ \todo{Peter: Why do you say general gamma?  I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}  \todo{Peter: also, its not clear to me that this should be said right here.  I think we may want to say a bit more about what's already known instead of going directly to what we have done}.  In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
\cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$. In order to find generators and relations for $M(\Gamma)$, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
category, using a generalization of the GAGA principle. By
\cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of
categories between orbifold curves and log stacky curves over $\BC$.
Hence, for the remainder of the paper, we will work in the
algebraic category. \todo{mention that we will use the language
of Weil divisors?}

@@

The goal of this paper is to provide a stricter bound on the
generator and relation degrees of log spin canonical rings
for all genera. Note that O'Dorney's bounds are asymptotically
tight for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
to the log spin curve case allows for lower bounds.
The main theorem of this paper is the following improved bound on
the degree of generators and relations of log spin canonical rings:

\todo{State for even weight modular forms attributed to VZB.}
\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use seperable stacky points} so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
log spin canonical ring

@@

\begin{rem}
In fact, the theorem only needs to assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
\todo{combine the below chunk with the near-duplicate section
in the introduction}
A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
geometrically-connected Deligne-Mumford stack of dimension $1$ over
$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
its stabilizers are coprime to char $k$. Throughout this paper,
stacky curves will be assumed to be tame and $k$ will always be
algebraically closed. We also assume that the stacky curves are
separably rooted, i.e. the residue field of each stacky points
is separable. The language of stacks will be omitted in
this paper, as it is sufficient to view stacky curves and related
objects $\sx$ as a scheme whose associated divisor group allows for
a finite number of \textbf{stacky points} which may be viewed
heuristically as ``fractional points''. See Voight and
Zureick-Brown for more thorough treatment of these definitions
\cite[Chapter 5]{vzb:stacky}. \todo{again, not quite viewing as a
scheme}

@@

\begin{defn}
If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\todo{cite lemma 5.4.7 from VZB maybe?}

@@

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_L$ to
represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^{th}$
degree component of $R$.

@@

\subsection{Junk}
\todo{add this back into the intro}
This is stuff that has been moved out of the introduction to possibly
be retooled for this section.

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$).
\end{enumerate}
\end{lem}

\begin{proof}
{\bf Part (a):}
By
Equation ~\ref{eqn:deg1-sat-ind}, for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

\begin{defn}
\label{defn:admissible}
Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
curves, with the same coarse space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

@@

\begin{align*}
	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle
	x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
\end{align*}
